\documentclass[12pt,a4paper,sans]{moderncv}   

\moderncvstyle{banking}                             
\moderncvcolor{blue}                               

\usepackage{anyfontsize}
\usepackage[scale=0.85]{geometry}

\name{Patrik}{Gerber}
\address{Corpus Christi College, Merton Street}{Oxford}{United Kingdom}
\phone[mobile]{+xx xx xxxxxxx}
\email{xxxx@xxxx.com}     

\begin{document}
\nopagenumbers{}

\makecvtitle

\vspace{-20mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\cventry{October 2015--present}{Mathematics and Statistics MMath}{University of Oxford}{Oxford, UK}{}{\fontsize{12}{0}\selectfont Triple First-class honours, with main areas of study being Statistics, Probability and Analysis. }

\vspace{3mm}

\cventry{September 2011--June 2015}{High School student}{Bolyai Janos Grammar School}{Kecskemet, Hungary}{}{\fontsize{12}{0}\selectfont 
Took 6 subjects at the Hungarian Matura with an average of 96\%}

\vspace{-3mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\cventry{June 2018--present}{Institute for Pure and Applied Mathematics, UCLA}{Research Intern}{Los Angeles, California}{}{\fontsize{12}{0}\selectfont Working in Deep Reinforcement Learning, specifically looking at improving the robustness of standard algorithms in the face of changes in the learning environment. We utilize Tensorflow as our Deep Learning framework, using video games such as the classic Atari games as our benchmarks.} 

\vspace{3mm}

\cventry{July 2017--September 2017}{Softwire}{Software Engineering intern}{London, UK}{}{\fontsize{12}{0}\selectfont Worked in a team of 6 building a web application from scratch using Typescript, with Angular and Firebase.
Gained familiarity with Git, CI pipelines, unit testing and agile software development principles, and learnt to
adapt to new technologies quickly and independently.}

\vspace{3mm}
\cventry{October 2015--June 2016}{Corpus Christi College Commemoration Ball}{IT Officer}{Oxford, UK}{}{\fontsize{12}{0}\selectfont Created and maintained the event's website.}

\vspace{-3mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AWARDS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}

\cventry{July 2018}{Department of Statistics, University of Oxford}{Department of Statistics Prize}{Oxford, UK}{}{\fontsize{12}{0}\selectfont Awarded to the top student studying Mathematics \& Statistics }

\vspace{3mm}

\cventry{July 2017}{Department of Mathematics, University of Oxford}{Gibbs prize}{Oxford, UK}{}{\fontsize{12}{0}\selectfont Awarded to the top 2 students studying either Mathematics or Mathematics \& Statistics }

\vspace{3mm}

\cventry{March 2014}{XIII. National Piano Competition}{3rd prize}{Nyíregyháza, Hungary}{}{\fontsize{12}{0}\selectfont 
I competed in the 16-22 age division of the triannual competition.}

\vspace{3mm}

\cventry{March 2014}{Bolyai János Grammar School}{Bolyai prize}{Kecskemét, Hungary}{}{\fontsize{12}{0}\selectfont 
Awarded each year to one graduating student for their academic performance and good standing in the community.}

\vspace{-3mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SKILLS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\textbf{Programming languages} - {Most experience in Python, R; Have used Matlab, C++ and Typescript in the past}

\vspace{3mm}

\textbf{Frameworks and technologies} - {Most experience using Tensorflow and Git; Have used Firebase, Angular, Latex and Jenkins in the past}

\vspace{3mm}

\textbf{Data Analyis} - {Taken multiple theoretical and applied statistics courses, familiar with basics of the data analysis pipeline}

\vspace{3mm}

\textbf{Languages} - {Hungarian (native), English (proficient, IELTS 8.5), German (proficient, ÖSD C1 96/100)}

\vspace{3mm}

\textbf{Music} - {As an avid amateur pianist for 15 years, I've had the opportunity to play with various other musicians and even a small orchestra. I enjoy playing classical music from the 20th and 19th centuries mainly. }

\end{document}
